Data Preparation

### 2019-03-12 Data Preparation.Rmd

## List of AoD's and Assessments
First, we import the spreadsheet with information pertraining the Aims of the Degree (AoD) and Assessments from the drive and save it under `lists_brut`. ` lists_brut` contains 4 columns, under which we find the `19` types of assessment, the `18` aims of the degree (AoD) of the degree, and  two columns containing binary vectors indicating which assessment types and AoD  we will consider when ploting the data[^1].
Then we create a list with this same columns, but instead of having binary vectors for the plots, we keep vectors of only the names of relevant assessments and AoDs for the plots (`Assessment_plot`adnd `AoD_plot` respectively). We also any imported emtpy cells.
```{r list_AoD_assessment}
list_AoD_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347') %>%
  map(na.omit)

@@

```{r d_assessment}
d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
  mutate_if(
    .predicate = is.numeric,
    .funs      = as.logical
    ) %>%

  # Transform data into tidy format to facilitate manipulation
  gather(
    key   = Assessment, 
    value = assessment_covered,
    Paper : Participation
    ) %>%
  filter(
    assessment_covered
    ) %>%
  select(
    - c(assessment_covered, `Comment on Assessment`)
    ) %>%
  print
```

```{r d_AoD_from_ILO}
d_AoD_from_ILO <- d_ILO %>%
  rename(
    ILO = Objectives
    ) %>%
  mutate_if(
    .predicate = is.numeric,
    .funs      = as.logical
    ) %>%

  # Transform data into tidy format to facilitate manipulation
  gather(
    key   = AoD, 
    value = AoD_covered,
    `Matrix Complete` : `Intercultural Skills`
    ) %>%
  filter(
    AoD_covered
    ) %>%
  select(
    - c(AoD_covered, Comments, Comments_for_Jeroen)
    ) %>%
  print
```

## Textual Data
In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues. The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.
```{r catalogues, cache = TRUE}
# helper function
read_in_pdfs <- function(file){

@@

    # turn corpus into a list to facilitate manipulation
    as.list %>%
    unname

d_text <- list()

@@

```{r manuals, cache = TRUE}
# helper functions
extract_code <- function(string) string %>% str_sub(start = 1, end = 7)

d_text$manuals <- "./Input/Manuals 2017-18" %>%
  read_in_pdfs %>%

@@

  transmute(
    `Course ID` = manuals %>% map(function(x) x$meta$id) %>% map_chr(extract_code),
    year        = "2017-2018",
    text        = manuals %>% map(content) %>% map_chr(str_c, collapse = " ")
    ) %>%
  print

@@

```{r d_transcript, cache = TRUE}
col_parsing <- cols(
  `Student Number`                      = "c",
  `Program (Abbreviation)`              = "c",
  `Appraisal Status`                    = "c",
  `Module Booking Reason (Description)` = "c",
  `Object name`                         = "c",
  `Start date`                          = "c",
  `End Date`                            = "c"
  )

read_csv_own_parsing <- function(file) file %>% read_csv( col_types = col_parsing) # helper function

d_transcript <- paste0("Input/Raw Grades/grades", 1:2, ".csv") %>%
  map(read_csv_own_parsing) %>%
  bind_rows

@@

```{r map_assessment_AoD}
map_assessment_AoD <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216') %>%
  mutate_if(
    .predicate = is.numeric,
    .f         = as.logical
    ) %>%

  # Transform data into tidy format to facilitate manipulation
  gather(
    key   = AoD, 
    value = AoD_covered,
    `Matrix Complete` : `Intercultural Skills`
    ) %>%
  filter(
    AoD_covered
    ) %>%
  select(
    - AoD_covered
    ) %>%
  arrange(
    Assessment
    ) %>%
  print
```

Now that we have the matrix `map_assessment_AoD`, we want to find out which AoDs are covered by a course through its assessments. To do this we create an empty tibble `d_AoD_assessment` to store which assessment is covered by each course, and which AoD said assessment covers.Then, we fill in the information with a loop.
In the loop, we first extract a row of `d_assessment` and save it as `observation`. Then, we determine the corresponding assessment which we save as `assessment`. Then, we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
```{r d_AoD_assessment}
d_AoD_from_assessment <- d_assessment %>%
  left_join(
    map_assessment_AoD,
    by = "Assessment"
    ) %>%
  print

@@

#### Combining AoD from ILOs and from assessments
Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `distinct` in case a course covers an AoD with both its ILOS and its assessments.
```{r rbind d_AoD_ILO and d_AoD_assessment}
d_AoD <- rbind(
  d_AoD_from_ILO        %>% select(`Course ID`, AoD),
  d_AoD_from_assessment %>% select(`Course ID`, AoD)
  ) %>%
  distinct %>%
  arrange(
    `Course ID`
    ) %>%
  print

@@

Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. For this we create the following three tibbles:
1) `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains.
2) `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers. 
3) `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. 
Then we use a `full_join` to add these variables to the tibble `d_course`.
```{r d_course detail}
# helper function
count_and_paste <- function(data, var, colnam1, colnam2){

  data %>%
    group_by(
      `Course ID`
      ) %>%
    summarize(
      !!ensym(colnam1) := n_distinct(!!enquo(var)),
      !!ensym(colnam2) := str_c(!!enquo(var), collapse = ", ")
    )

@@

# helper function
join_by_course_ID <- function(data1, data2){

  data1 %>%
    left_join(
      y = data2,
      by = "Course ID"
    )

```{r join d_course_detail}
d_course <- d_course %>%
  join_by_course_ID( d_AoD %>% count_and_paste(AoD, n_AoD, `AoD Covered`) %>% print) %>%
  join_by_course_ID( d_assessment %>% count_and_paste(Assessment, n_assessment, `Assessments Covered`) ) %>%
  join_by_course_ID( d_ILO %>% count_and_paste(Objectives, n_ILO, `ILO Covered`        ) ) %>%
  select(
    `Course ID`, `Course Title`, Cluster,
    n_ILO,
    n_assessment, `Assessments Covered`,
    n_AoD, `AoD Covered`,
    everything()
    ) %>%
  print

@@

The undegraduate research courses (*UGR-*) are only present at the `3000` level (advanced level). Yet, these course are also offered at the `2000` level (intermediate level). We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
```{r create UGR2000}
UGR_2000 <- d_course %>%
  filter(
    `Course ID` %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")
    ) %>%
  mutate(
    `Course ID` = case_when(
      `Course ID` == "UGR3001" ~ "UGR2001",
      `Course ID` == "UGR3002" ~ "UGR2002",
      `Course ID` == "UGR3003" ~ "UGR2003",
      `Course ID` == "UGR3005" ~ "UGR2005"
      )
    ) %>%
  print

@@

print(d_course %>% filter(str_detect(`Course ID`, "UGR") ) )

@@

Finally, we add a series of informative variable at the course level.
```{r d_course additional info}
d_course <- d_course %>%
  separate(
    col     = `Course ID`,
    into    = c("Letters", "Number"),
    sep     = 3,
    remove  = FALSE,
    convert = TRUE
    ) %>%
  mutate(
    Level   = case_when(
      between(Number, 1000, 1999) ~ "Introductory",
      between(Number, 2000, 2999) ~ "Intermediate",
      between(Number, 3000, 3999) ~ "Advanced"    )
    ) %>%
  select(`Course ID`, Letters, Number, Level, everything()
    ) %>%
  print
```

@@

```{r extract_description, eval = FALSE}
extract_description <- function(overview){

@@

    mutate(
      is_start_descrip = line %>% is_start_descrip,
      is_end_descrip   = line %>% is_end_descrip # Having several ends (e.g. "literature" and "instructional format") is ok because we only use the first (cumany)
      ) %>%

    # filter the description section
    mutate(
      is_after_start_descrip = cumany( is_start_descrip),
      is_before_end_descrip  = cumall(!is_end_descrip  ),
      is_descrip             = is_after_start_descrip & is_before_end_descrip
      ) %>%
    filter(is_descrip, !is_start_descrip, !is_end_descrip) %>%

    summarise(description = str_c(line, collapse = " ")) %>%
    pull

@@

```{rclean_period}
clean_period <- function(period){

@@

# Save Data
```{r}
save(d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO,
     file = "Output/data_general.RDATA")
save(d_transcript,
     file = "Output/data_pillar_1.RDATA")
save(d_text, d_course, d_transcript,
     file = "Output/data_pillar_2.RDATA")
```

>>>>

## List of AoD's and Assessments
First, we import the spreadsheet with information pertraining the Aims of the Degree (AoD) and Assessments from the drive and save it under `lists_brut`. ` lists_brut` contains 4 columns, under which we find the `19` types of assessment, the `18` aims of the degree (AoD) of the degree, and  two columns containing binary vectors indicating which assessment types and AoD  we will consider when ploting the data[^1].
Then we create a list with this same columns, but instead of having binary vectors for the plots, we keep vectors of only the names of relevant assessments and AoDs for the plots (`Assessment_plot`adnd `AoD_plot` respectively). We also any imported emtpy cells.
```{r list_AoD_assessment}
list_AoD_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347') %>%

  map(na.omit)

@@

```{r d_assessment}
d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%

  mutate_if(is.numeric, as.logical) %>%

  # Transform data into tidy format to facilitate manipulation
  gather(
    key   = Assessment, 
    value = assessment_covered,
    Paper : Participation
    ) %>%

  filter(assessment_covered) %>%

  select(- c(assessment_covered, `Comment on Assessment`)) %>%

  print
```

```{r d_ILO}
d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050')
```

```{r d_AoD_from_ILO}
d_AoD_from_ILO <- d_ILO %>%

  rename(ILO = Objectives) %>%

  mutate_if(is.numeric, as.logical) %>%

  # Transform data into tidy format to facilitate manipulation
  gather(
    key   = AoD, 
    value = AoD_covered,
    `Matrix Complete` : `Intercultural Skills`
    ) %>%

  filter(AoD_covered) %>%

  select(- c(AoD_covered, Comments, Comments_for_Jeroen)) %>%

  print
```

## Textual Data
In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues. The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.

```{r read_in_pdfs}
# helper function
read_in_pdfs <- function(file){

@@

    # turn corpus into a list to facilitate manipulation
    as.list %>%

    unname

```{r catalogues, cache = TRUE}
d_text <- list()

@@

```{r extract_code}
# helper functions
extract_code <- function(string) string %>% str_sub(start = 1, end = 7)
```

```{r manuals, cache = TRUE}
d_text$manuals <- "./Input/Manuals 2017-18" %>%

  read_in_pdfs %>%

@@

  transmute(
    `Course ID` = manuals %>% map(function(x) x$meta$id) %>% map_chr(extract_code),
    year        = "2017-2018",
    text        = manuals %>% map(content) %>% map_chr(str_c, collapse = " ")
    ) %>%

  print

@@

```{r read_csv_own_parsing}
# set up
col_parsing <- cols(
  `Student Number`                      = "c",
  `Program (Abbreviation)`              = "c",
  `Appraisal Status`                    = "c",
  `Module Booking Reason (Description)` = "c",
  `Object name`                         = "c",
  `Start date`                          = "c",
  `End Date`                            = "c"
  )

# helper function
read_csv_own_parsing <- function(file) file %>% read_csv(col_types = col_parsing)
```

```{r d_transcript, cache = TRUE}
d_transcript <- paste0("Input/Raw Grades/grades", 1:2, ".csv") %>%
  map(read_csv_own_parsing) %>%
  bind_rows

@@

```{r map_assessment_AoD}
map_assessment_AoD <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216') %>%

  mutate_if(is.numeric, as.logical) %>%

  # Transform data into tidy format to facilitate manipulation
  gather(
    key   = AoD, 
    value = AoD_covered,
    `Matrix Complete` : `Intercultural Skills`
    ) %>%

  filter(AoD_covered) %>%

  select(- AoD_covered) %>%

  arrange(Assessment) %>%

  print
```

Now that we have the matrix `map_assessment_AoD`, we want to find out which AoDs are covered by a course through its assessments. To do this we create an empty tibble `d_AoD_assessment` to store which assessment is covered by each course, and which AoD said assessment covers.Then, we fill in the information with a loop.
In the loop, we first extract a row of `d_assessment` and save it as `observation`. Then, we determine the corresponding assessment which we save as `assessment`. Then, we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
```{r d_AoD_assessment}
d_AoD_from_assessment <- d_assessment %>%

  left_join(map_assessment_AoD, by = "Assessment") %>%

  print

@@

#### Combining AoD from ILOs and from assessments
Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `distinct` in case a course covers an AoD with both its ILOS and its assessments.
```{r rbind d_AoD_ILO and d_AoD_assessment}
d_AoD <- rbind(
  d_AoD_from_ILO        %>% select(`Course ID`, AoD),
  d_AoD_from_assessment %>% select(`Course ID`, AoD)
  ) %>%

  distinct %>%

  arrange(`Course ID`) %>%

  print

@@

Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. For this we create the following three tibbles:
1) `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains.
2) `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers. 
3) `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. 
Then we use a `full_join` to add these variables to the tibble `d_course`.
```{r d_course detail}
# helper function
count_and_paste <- function(df, var, colnam1, colnam2){

  df %>%

    group_by(`Course ID`) %>%

    summarize(
      !!ensym(colnam1) := n_distinct(!!enquo(var)),
      !!ensym(colnam2) := str_c(!!enquo(var), collapse = ", ")
      )

@@

# helper function
join_by_course_ID <- function(df1, df2) left_join(df1, df2, by = "Course ID")
```

```{r join d_course_detail}
d_course <- d_course %>%

  join_by_course_ID( d_AoD %>% count_and_paste(AoD, n_AoD, `AoD Covered`) %>% print) %>%

  join_by_course_ID( d_assessment %>% count_and_paste(Assessment, n_assessment, `Assessments Covered`) ) %>%

  join_by_course_ID( d_ILO %>% count_and_paste(Objectives, n_ILO, `ILO Covered`        ) ) %>%

  select(
    `Course ID`, `Course Title`, Cluster,
    n_ILO,
    n_assessment, `Assessments Covered`,
    n_AoD, `AoD Covered`,
    everything()
    ) %>%

  print

@@

The undegraduate research courses (*UGR-*) are only present at the `3000` level (advanced level). Yet, these course are also offered at the `2000` level (intermediate level). We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
```{r create UGR2000}
UGR_2000 <- d_course %>%

  filter( `Course ID` %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%

  mutate(
    `Course ID` = case_when(
      `Course ID` == "UGR3001" ~ "UGR2001",
      `Course ID` == "UGR3002" ~ "UGR2002",
      `Course ID` == "UGR3003" ~ "UGR2003",
      `Course ID` == "UGR3005" ~ "UGR2005"
      )
    ) %>%

  print

@@

# print UGR course
print(d_course %>% filter(str_detect(`Course ID`, "UGR") ) )

@@

Finally, we add a series of informative variable at the course level.
```{r d_course additional info}
d_course <- d_course %>%

  separate(
    col     = `Course ID`,
    into    = c("Letters", "Number"),
    sep     = 3,
    remove  = FALSE,
    convert = TRUE
    ) %>%

  mutate(
    Level   = case_when(
      between(Number, 1000, 1999) ~ "Introductory",
      between(Number, 2000, 2999) ~ "Intermediate",
      between(Number, 3000, 3999) ~ "Advanced"    )
    ) %>%

  select(`Course ID`, Letters, Number, Level, everything()
    ) %>%

  print
```

@@

```{r extract_description}
extract_description <- function(overview){

@@

    mutate(
      is_start_descrip = line %>% is_start_descrip,
      is_end_descrip   = line %>% is_end_descrip # Having multiple ends (e.g. "literature" and "instructional format") is ok because we only use the first (cumany)
      ) %>%

    # filter the description section
    mutate(
      is_after_start_descrip = cumany( is_start_descrip),
      is_before_end_descrip  = cumall(!is_end_descrip  ),
      is_descrip             = is_after_start_descrip & is_before_end_descrip
      ) %>%

    filter(is_descrip, !is_start_descrip, !is_end_descrip) %>%

    summarise(description = str_c(line, collapse = " ")) %>%

    pull

@@

```{r clean_period}
clean_period <- function(period){

@@

# Save Data
```{r}
save(
  d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO,
  file = "Output/data_general.RDATA"
  )

save(d_transcript, file = "Output/data_pillar_1.RDATA")

save(d_text, d_transcript, file = "Output/data_pillar_2.RDATA")
```
